COVIDcast Indicators figures and tables

### 2021-10-04 indicators/code/indicator-paper-figures.Rmd
Axes labels for Fig 7

w_cdc %>%
  filter(best_pop > 0, sample_size >= 250) %>%
  ggplot(aes(x = value, y = Series_Complete_18PlusPop_Pct, color = REGION)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(labels = label_percent(scale = 1)) +
  scale_y_continuous(labels = label_percent(scale = 1)) +
  theme_bw() +
  labs(x = "Estimated % willing to be vaccinated, 2021-01-20",
       y = "% vaccinated on 2021-07-20", color = "Region") +
  theme(legend.pos = "bottom", legend.direction = "horizontal")

>>>>

w_cdc %>%
  filter(best_pop > 0, sample_size >= 250) %>%
  ggplot(aes(x = value, y = Series_Complete_18PlusPop_Pct, color = REGION)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(labels = label_percent(scale = 1)) +
  scale_y_continuous(labels = label_percent(scale = 1)) +
  theme_bw() +
  labs(x = "% willing to be vaccinated on January 20, 2021",
       y = "% vaccinated on July 20, 2021", color = "Region") +
  theme(legend.pos = "bottom", legend.direction = "horizontal")
